---
title: "Post Analysis"
author: "lushi"
date: "23/09/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(dplyr)
library(ggplot2)
library(xtable)
library(Hmisc)
library(RcmdrMisc)
library(stargazer)
library(fastDummies)
library(lubridate)
library(zoo)
#devtools::install_github("cardiomoon/ggiraphExtra")
require(moonBook)
require(ggiraphExtra)
require(anytime)
require(tidyr)
library("gridExtra")
library("tseries")
library("aTSA")
library("pracma")

```


```{r readanno}
path = '/Users/lucia/hawksworth/pandemic_anxiety/data/posts/'
#path = "/home/lucia/Documents/lucia/pandemic_anxiety/data/posts/"
setwd(path)

covid <- read.csv('COVID19_support_postids_posts.csv',  stringsAsFactors = FALSE)
cle <-  covid[!duplicated(covid$post_id), ]

```

## get annotationn
Merge all the annotation data
```{r readanno}
path = '/Users/lucia/hawksworth/pandemic_anxiety/data/anno_test/data'
#path = "/home/lucia/Documents/lucia/pandemic_anxiety/data/anno_test/data/"
setwd(path)
#this is the path for the final annotation data 
read_all_files <- function(){
  all_files_df <- dir(pattern = "*.csv")
  list_of_frames <- lapply(all_files_df, read.csv)
  all <- do.call("rbind", list_of_frames)
  clean <-  all[!duplicated(all$post_id), ]
  return (clean)

}
anno_file <- read_all_files()
anno_file$text <- NULL
anno_file$title <- NULL


```

# merge the missing annotations with mine 
```{r readanno}
path = '/Users/lucia/hawksworth/pandemic_anxiety/data/anno_test/lucia/'
#path = "/home/lucia/Documents/lucia/pandemic_anxiety/data/anno_test/lucia/"
setwd(path)

aug <- read.csv('lucia_aug.csv')
sept <- read.csv('lucia_sept.csv')
lucia <- rbind(aug, sept)
#lucia

anno_file2 <- merge(anno_file,lucia, by='post_id', all.y = TRUE)
anno_file2[is.na(anno_file2 )] <- 0

write.csv(anno_file2, 'remain_data.csv')
write.csv(anno_file, 'all_data.csv')

## merge other variables with annotation

```

```{r readall}
path = '/Users/lucia/hawksworth/pandemic_anxiety/data/anno_test/'
#path = "/home/lucia/Documents/lucia/pandemic_anxiety/data/anno_test/"
setwd(path)

anno_file <- read.csv('all_data_final.csv')
anno_file <-  anno_file[!duplicated(anno_file$post_id), ]
```


```{r readall}

#clean  <- read_all_files()
annotation <- merge(anno_file, cle, all.x= TRUE, by = 'post_id')
#Link health infected with Break_guideline and health_work
annotation$health_infected <- ifelse(annotation$break_guideline == 1, 1, annotation$health_infected)

annotation$health_infected <- ifelse(annotation$health_work == 1, 1, annotation$health_infected)

```

# select timeline and get monthly percentage

```{r timeline}
annotation$date<- as.Date(annotation$time, format = "%m/%d/%Y/%H:%M:%S")
mar <- annotation[annotation$date > '2020-02-1' & annotation$date < '2020-03-31' ,]
apr <- annotation[annotation$date > '2020-04-1' & annotation$date < '2020-04-30' ,]
may <- annotation[annotation$date > '2020-05-1' & annotation$date < '2020-05-31' ,]
jun <- annotation[annotation$date > '2020-06-1' & annotation$date < '2020-06-30' ,]
july <- annotation[annotation$date > '2020-07-1' & annotation$date < '2020-07-31' ,]
aug <- annotation[annotation$date > '2020-08-1' & annotation$date < '2020-08-31' ,]
sept <- annotation[annotation$date > '2020-09-1' & annotation$date < '2020-09-30' ,]
oct <- annotation[annotation$date > '2020-10-1' & annotation$date < '2020-10-31' ,]

#apply(mar[,2:17], 2, table)

monthly_val <- function(var){
  result = vector(mode = "numeric")
  month <- c("mar", "apr", "may" ,"jun","july", "aug", "sept", "oct")
  for (i in month){
    if (i== 'mar'){
      i <- assign(i, mar)
    }
     else if (i== 'apr'){
      i <- assign(i, apr)
     }
    else if (i== 'may'){
      i <- assign(i, may)
    }
    else if (i== 'jun'){
      i <- assign(i, jun)
    }
    else if (i== 'july'){
      i <- assign(i, july)
    }
    
    else if (i== 'aug'){
      i <- assign(i, aug)
    }
    
    else if (i== 'sept'){
      i <- assign(i, sept)
    }
    
    else if (i== 'oct'){
      i <- assign(i, oct)
    }
    t_mar <- table(i[,c(var)])
    
    # some categories has zero 1
    if (length(t_mar) > 1){
    val <- t_mar[[2]]/nrow(i)
    result <-append(result, val)
    } else{
      result <-append(result, 0)
      
    }
    
    
  }
  result_df <- as.data.frame(matrix(result, ncol=1, byrow = T))
  result_df$month <- c(3, 4, 5, 6, 7, 8, 9, 10)
  colnames(result_df) <- c('doc_per', 'month')
  result_df$varname <- var
 return (result_df)
}


finance <- monthly_val('financial_career')
quar_social <- monthly_val('quar_social')
health_infected <- monthly_val('health_infected')
break_guideline <- monthly_val('break_guideline')
health_work <- monthly_val('health_work')
mental <- monthly_val('mental_health')
death <- monthly_val('death')
traveling <- monthly_val('travelling')
future <- monthly_val('future')


all_data <- bind_rows(
  finance, quar_social, health_infected, break_guideline, health_work, mental, death, traveling, future)
```


#plot monthly percentage, line plot
```{r plots}
ggplot(all_data, aes(month)) + 
  geom_line(aes(y = doc_per, colour = varname), size= 1) +
   scale_color_brewer(palette="Set1")+ 
  theme(text = element_text(size=20)) + theme(legend.position="bottom", legend.box = "horizontal")


```


#plot monthly percentage
```{r plots}
plot_anxiety_content <- function(df, title){ 
  ggplot(df, aes(x=month, y=doc_per)) + 
  geom_bar(stat = "identity",  fill = "steelblue") +
  ggtitle(title)
}

fa <- plot_anxiety_content(finance, "Finance")
qua <- plot_anxiety_content(quar_social, 'Quaratine')
infect <- plot_anxiety_content(health_infected, 'Infect')
break_g <- plot_anxiety_content(break_guideline, 'Break Guideline')
work <- plot_anxiety_content(health_work, 'Work Risks')
death <- plot_anxiety_content(death, 'Death')
#travel <- plot_anxiety_content(traveling, 'Traveling')
mental <- plot_anxiety_content(mental, 'Mental Health')
future <- plot_anxiety_content(future, 'Future')

gridExtra::grid.arrange(fa, qua, infect, break_g, work, death, mental, future, nrow = 2) 
```

#subject of worry correlation



```{r corstars}
corstars <-function(x, method=c("pearson", "spearman"), removeTriangle=c("upper", "lower"),
                     result=c("none", "html", "latex")){
    #Compute correlation matrix
    require(Hmisc)
    x <- as.matrix(x)
    correlation_matrix_adj<-rcorr.adjust(x, type=method[1])
    correlation_matrix<-rcorr(x, type=method[1])
    R <- correlation_matrix$r # Matrix of correlation coeficients
    p1 <- correlation_matrix_adj$R[3][1]
    p <- p1$P# Matrix of p-value 
    
    ## Define notions for significance levels; spacing is important.
    mystars <- ifelse(p < .0001, "****", ifelse(p < .001, "*** ", ifelse(p < .01, "**  ", ifelse(p < .05, "*   ", "    "))))
    
    
    
    ## trunctuate the correlation matrix to two decimal
    R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]
    
    ## build a new matrix that includes the correlations with their apropriate stars
    Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
    diag(Rnew) <- paste(diag(R), " ", sep="")
    rownames(Rnew) <- colnames(x)
    colnames(Rnew) <- paste(colnames(x), "", sep="")
    
    ## remove upper triangle of correlation matrix
    if(removeTriangle[1]=="upper"){
      Rnew <- as.matrix(Rnew)
      Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove lower triangle of correlation matrix
    else if(removeTriangle[1]=="lower"){
      Rnew <- as.matrix(Rnew)
      Rnew[lower.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove last column and return the correlation matrix
    Rnew <- cbind(Rnew[1:length(Rnew)-1])
    if (result[1]=="none") return(Rnew)
    else{
      if(result[1]=="html") print(xtable(Rnew), type="html")
      else print(xtable(Rnew), type="latex") 
    }
} 

```



# get correlation table
```{r worry}
cor_var<- annotation[,2:16]
cor_var$info_sharing <- NULL
cor_var$info_sharing_personal <- NULL
cor_var$rant <- NULL
cor_var$other <- NULL
cor_var$mourn_death <- NULL
#cor_var[cor_var$mental_health == 'z']
cor_var$mental_health<- as.numeric(cor_var$mental_health)
cor_var <- cor_var[!is.na(cor_var$mental_health), ]

mcor <- corstars(cor_var, "pearson")


upper<-mcor
upper[upper.tri(mcor)]<-""
upper<-as.data.frame(upper)
upper
xtable(upper)
```


# get adjusted p values
```{r corstars}
cor_var <- as.matrix(cor_var)
correlation_matrix <- rcorr.adjust(cor_var, "spearman")
p <- correlation_matrix$P

```


# regression on anxiety
```{r worry}
annotation1 <- annotation
annotation1$anxiety[annotation1$anxiety == 0] <- 1

fit <- glm(anxiety ~ financial_career + quar_social + health_infected + break_guideline + health_work +mental_health + death + travelling + future
                  , data=annotation1)  # build linear regression model on full data
summary(fit)
stargazer(fit)

```

# plot regression 
```{r worry plot}

ggPredict(fit1,se=TRUE,interactive=TRUE,digits=3)
```



# language intensity plot

```{r worry plot}

anxiety <- annotation[ ,c('anxiety', 'date')]
dum <- fastDummies::dummy_cols(anxiety$anxiety)
colnames(dum) <- c('orginal','none','low','high')
dum$date <- anxiety$date

mar <- dum[dum$date > '2020-02-1' & dum$date < '2020-03-31' ,]
apr <- dum[dum$date  > '2020-04-1' & dum$date  < '2020-04-30' ,]
may <- dum[dum$date  > '2020-05-1' & dum$date  < '2020-05-31' ,]
jun <- dum[dum$date  > '2020-06-1' & dum$date  < '2020-06-30' ,]
july <- dum[dum$date > '2020-07-1' & dum$date < '2020-07-31' ,]
aug <- dum[dum$date > '2020-08-1' & dum$date < '2020-08-31' ,]
sept <- dum[dum$date > '2020-09-1' & dum$date < '2020-09-30' ,]
oct <- dum[dum$date > '2020-10-1' & dum$date < '2020-10-31' ,]

none <- monthly_val('none')
low <- monthly_val('low')
high <- monthly_val('high')


all_ans<- bind_rows(
  none, low, high)

ggplot(all_ans, aes(month)) + 
  geom_line(aes(y = doc_per, colour = varname), size= 2) +
   scale_color_brewer(palette="Set1")+ 
  theme(text = element_text(size=20)) +
  theme(legend.position="bottom", legend.box = "horizontal")



```



# anxiety level
Here we compute anxiety = number of subjects of worry * language intensity

```{r anxiety plot}

annotation$anxiety[annotation$anxiety == 0] <- 1
#annotation$anxiety <- annotation$anxiety+1
annotation$anxiety_level <- rowSums(annotation[,3:16] > 0) * annotation$anxiety


annotation$date <- as.Date(annotation$date)
annotation %>% dplyr::group_by(month=floor_date(date, "week")) %>%
  dplyr::summarize(amount=mean(anxiety_level)) -> grouped

grouped <- grouped[complete.cases(grouped), ]

ggplot(grouped, aes(x=month, y=amount)) +
  geom_line(aes(y = amount), size= 2) + 
  theme(text = element_text(size=20)) +
  ylab("anxiety level")

```


#anxiety level of predicted labels
```{r anxiety plot}
path = '/Users/lucia/hawksworth/pandemic_anxiety/results/prediction_result_2500/'
#path = "/home/lucia/Documents/lucia/pandemic_anxiety/results/prediction_result_2500/"
setwd(path)
annotation_pred <- read.csv('all_prediction_results.csv')
#annotation_pred$anxiety <- annotation_pred$prediction_anxiety+1
annotation_pred$anxiety_level <- rowSums(annotation[,3:11] > 0) * annotation_pred$prediction_anxiety

# merge with time 
time <- cle[,c('post_id', 'time')]
anno_pre <- merge(time, annotation_pred, by = 'post_id', all.y = TRUE)
anno_pre <- anno_pre[complete.cases(anno_pre), ]



anno_pre$date <- anydate(anno_pre$time)
anno_pre <- anno_pre[anno_pre$date > '2020-03-1', ]
anno_pre %>% dplyr::group_by(month=floor_date(date, "week")) %>%
  dplyr::summarize(amount=mean(anxiety_level)) -> grouped2

grouped2 <- grouped2[complete.cases(grouped2), ]


#plot human and annotated
grouped2$label <- "machine"
grouped$label <- 'human'
anxiety_level <- rbind(grouped2, grouped)


# check stationary
kpss.test(grouped2$amount) #non stationary
kpss.test(grouped$amount)#non stationary

grouped3 <- grouped2[grouped2$amount < '2020-11-1', ]

#detrend
grouped3$value_d <- detrend(grouped3$amount, tt = 'linear', bp = c())
grouped$value_d <- detrend(grouped$amount, tt = 'linear', bp = c())


# check correlation
ts_cor <- ccf(as.numeric(grouped3$value_d), as.numeric(grouped$value_d), type="correlation")

# check periodicity 

ptestg(grouped2$amount,method = "Fisher")

ggplot(grouped2, aes(x=month, y=amount)) +
  geom_line(aes(y = amount), size= 2) + 
  theme(text = element_text(size=20)) +
  ylab("anxiety level")


ggplot(anxiety_level, aes(month)) + 
  geom_line(aes(y = amount, colour = label), size= 1) +
   scale_color_brewer(palette="Set1")+ 
  xlab("") + ylab("value") +
  theme(text = element_text(size=20)) + theme(legend.position="bottom", legend.box = "horizontal")



```


#plot monthly percentage, line plot
```{r plots}
anno_pre %>% dplyr::group_by(month=floor_date(date, "month")) %>%
  dplyr::summarize(finance=mean(prediction_financial_career), quar=mean(prediction_quar_social), infected=mean(prediction_health_infected), guideline=mean(prediction_break_guideline), work=mean(prediction_health_work), mental=mean(prediction_mental_health), death=mean(prediction_death), travel=mean(prediction_travelling), future=mean(prediction_future)) -> grouped_var

grouped_var %>%  unite('value', 2:10, remove = FALSE) -> grouped_var2

df.long <- gather(grouped_var, varname, value, -month)


ggplot(df.long, aes(month)) + 
  geom_line(aes(y = value, colour = varname), size= 1) +
  # scale_color_brewer(palette="Set1")+ 
  scale_color_manual(values=c("#4DAF4A", "#F786BF", "#FF7F00", "#E41A1C", "#FFD700", "#A65628","#377EB8", "#696969", "#984EA3")) +
  theme(text = element_text(size=20)) + theme(legend.position="bottom", legend.box = "horizontal")

#green #4DAF4A,  "#A65628"brown, "#377EB8" blue, "#984EA3" purple, "#FF7F00 orange", "#FFFF33 yellow", "#E41A1C red", ,"#F781BF", "#F786BF"



anno_pre %>% dplyr::group_by(month=floor_date(date, "month")) %>%
  dplyr::summarize(finance=mean(prediction_financial_career), restrict=mean(prediction_quar_social), health=mean(prediction_health_infected), guideline=mean(prediction_break_guideline), work=mean(prediction_health_work), mental=mean(prediction_mental_health), death=mean(prediction_death), travel=mean(prediction_travelling),future=mean(prediction_future)) -> grouped_week

df.long.week <- gather(grouped_week, varname, value, -month)

ggplot(df.long.week, aes(month)) + 
  geom_line(aes(y = value, colour = varname), size= 1) +
   scale_x_date(date_labels="%b %Y",date_breaks  ="1 month") + 
  # scale_color_brewer(palette="Set1")+ 
  scale_color_manual(values=c("#4DAF4A", "#F786BF", "#FF7F00", "#E41A1C", "#FFD700", "#A65628","#377EB8", "#696969", "#984EA3")) + 
  theme_bw() +
  #theme(text = element_text(size=20)) + theme(legend.position="bottom", legend.box = "horizontal")+
 theme(axis.text.x = element_text(angle = 60, vjust = 0.5), axis.title.x = element_blank())

   



```





time series cross correlation
```{r plots}


machine <- grouped2[grouped2$month < '2020-11-1', ]
human <- grouped
ccf(machine$amount, human$amount, type="correlation")

machine <- grouped2[grouped2$month < '2020-11-1', ]
human <- grouped

#compare SOW graph
ts_correlation <- function(machine_var, human_var) {
    machine <- df.long[df.long$varname == machine_var,]
    kpt <- kpss.test(machine$value)
    
    machine <- machine[machine$month < '2020-11-1', ]
    
    human <- all_data[all_data$varname == human_var,]
    human <- human[order(human$month),]
    
    #detrend
    machine$value_d <- detrend(machine$value, tt = 'linear', bp = c())
    human$value_d <- detrend(human$doc_per, tt = 'linear', bp = c())
    
    ts_cor <- ccf(as.numeric(machine$value_d), as.numeric(human$value_d), type="correlation")
    
    return (ts_cor)
    return (ccf(as.numeric(machine$value_d), as.numeric(human$value_d), type="correlation"))
}

#significantly positively correlated in x lags
ts_correlation('infected', 'health_infected') # one
ts_correlation('finance', 'financial_career') #
ts_correlation('quar', 'quar_social') # 
ts_correlation('guideline', 'break_guideline') #one
ts_correlation('work', 'health_work')
ts_correlation('mental', 'mental_health') # one
ts_correlation('death', 'death') #two
ts_correlation('travel', 'travelling') #one
ts_correlation('future', 'future')

#compare SOW graph
pearson_correlation <- function(machine_var, human_var) {
    machine <- df.long[df.long$varname == machine_var,]
    kpt <- kpss.test(machine$value)
    
    machine <- machine[machine$month < '2020-11-1', ]
    
    human <- all_data[all_data$varname == human_var,]
    human <- human[order(human$month),]
    
    pearson <- cor.test(as.numeric(machine$value), as.numeric(human$doc_per))
    
    return (pearson)
}

m <- pearson_correlation('infected', 'health_infected')


anno_pre %>% dplyr::group_by(month=floor_date(date, "week")) %>%
  dplyr::summarize(value=mean(prediction_anxiety)) -> grouped_anx_pre1

annotation %>% dplyr::group_by(month=floor_date(date, "week")) %>%
  dplyr::summarize(value=mean(anxiety)) -> grouped_anx

grouped_anx_pre <- grouped_anx_pre1[grouped_anx_pre1$month < '2020-11-1', ]

# check stationary
kpss.test(grouped_anx_pre$value) #stationary
kpss.test(grouped_anx$value)#stationary

#detrend
grouped_anx_pre$value_d <- detrend(grouped_anx_pre$value, tt = 'linear', bp = c())
grouped_anx$value_d <- detrend(grouped_anx$value, tt = 'linear', bp = c())

# check correlation
ts_cor <- ccf(as.numeric(grouped_anx_pre$value_d), as.numeric(grouped_anx$value_d), type="correlation")

grouped_anx_pre1$label <- "machine"
grouped_anx$label <- 'human'
grouped_anx$value_d <- NULL
lang_intensity <- rbind(grouped_anx_pre1, grouped_anx)

ggplot(lang_intensity, aes(month)) + 
  geom_line(aes(y = value, colour = label), size= 1) +
   scale_color_brewer(palette="Set1")+ 
  scale_x_date(date_labels="%b %Y",date_breaks  ="1 month") + 
  xlab("") +
  theme(text = element_text(size=20)) + theme(legend.position="bottom", legend.box = "horizontal") +
  theme_bw() +
   theme(axis.text.x = element_text(angle = 60, vjust = 0.5), axis.title.x = element_blank())



```


```{r plots}
path = '/Users/lucia/hawksworth/pandemic_anxiety/data/'
setwd(path)

covid_case <- read.csv('daily_tests.csv')

US<- covid_case[covid_case$Entity =='United States',]
colnames(US) <- c("Entity", "code", "day", "tests", "tests_perform", "cases","agg")

US$date <- as.Date(US$day, format = "%Y-%m-%d")
US %>% dplyr::group_by(month=floor_date(date, "week")) %>%
  dplyr::summarize(cases_count=mean(cases))-> cases_month

cases_month <- cases_month[cases_month$month > '2020-02-28' & cases_month$month < '2021-4-25', ]

#language intensity
anno_pre %>% dplyr::group_by(month=floor_date(date, "month")) %>%
  dplyr::summarize(value=mean(prediction_anxiety)) -> grouped_anx_pre_month


cases_month$cases <- 'cases'
colnames(cases_month) <- c('month', 'amount', 'label')


# check stationary
kpss.test(as.numeric(cases_month$amount)) #stationary with drift and trend   p<0.05

#anxiety level
machine_anxiety <- anxiety_level[anxiety_level$label == 'machine',]

human_anxiety <- anxiety_level[anxiety_level$label == 'human',]
#detrend
#cases_month$amount<- detrend(cases_month$amount, tt = 'linear', bp = c())
#machine_anxiety$amount <- detrend(machine_anxiety$amount, tt = 'linear', bp = c())

anxiety_level_all <- merge(machine_anxiety, cases_month, by = 'month', all.x = TRUE)
anxiety_level_all <- merge(anxiety_level_all, human_anxiety, by = 'month', all.x = TRUE)

# check correlation
ts_cor <- ccf(as.numeric(cases_month$amount), as.numeric(machine_anxiety$amount), type="correlation")

#anxiety_level_all <- rbind(machine_anxiety, cases_month)



coeff <- 100000
ggplot(anxiety_level_all, aes(x=month)) +
  
  geom_line(aes(y=amount.x), size=1, color="#009FB7") + 
  geom_line(aes(y=amount), size=1, color="#F6AE2D") + 
  geom_line(aes(y=amount.y/coeff), size=1, color="#FE4A49", linetype = "dashed") +
  scale_x_date(date_labels="%b %Y",date_breaks  ="1 month") + 
  
  
  scale_y_continuous(
    
    # Features of the first axis
    name = "Anxiety Index",
    
    # Add a second axis and specify its features
    sec.axis = sec_axis(~. *coeff, name="COVID cases")
  )+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5), axis.title.x = element_blank())


```


```{r plots}


US %>% dplyr::group_by(month=floor_date(date, "month")) %>%
  dplyr::summarize(cases_count=mean(cases))-> cases_month2
sow_all <- merge(grouped_var, cases_month2, all.x = TRUE)
colnames(sow_all) <- c("month", "career", "restrict", "health", "guideline","work","mental","death","travel","future", "cases_count")

coeff <- 300000
ggplot(sow_all, aes(x=month)) +
  
  geom_line(aes(y=career), size=1, color="#4DAF4A") + 
  geom_line(aes(y=restrict), size=1, color="#F781BF") + 
  geom_line(aes(y=health), size=1, color="#FF7F00") + 
  geom_line(aes(y=guideline), size=1, color="#E41A1C") + 
  geom_line(aes(y=work), size=1, color="#FFD700") + 
  geom_line(aes(y=mental), size=1, color="#A65628") + 
  geom_line(aes(y=death), size=1, color="#377EB8") + 
  geom_line(aes(y=travel), size=1, color="#696969") +
  geom_line(aes(y=future), size=1, color="#984EA3") +
  geom_line(aes(y=cases_count/coeff), size=2, color="blue", linetype = "dashed") +
  scale_x_date(date_labels="%b %Y",date_breaks  ="1 month") + 
  
  
  scale_y_continuous(
    
    # Features of the first axis
    name = "SOA",
    
    # Add a second axis and specify its features
    sec.axis = sec_axis(~. *coeff, name="COVID cases")
  )+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5), axis.title.x = element_blank())

#green #4DAF4A,  "#A65628"brown, "#377EB8" blue, "#984EA3" purple, "#FF7F00 orange", "#FFFF33 yellow", "#E41A1C red", ,"#F781BF", "#F786BF"
```

```{r plots}
annotation %>% dplyr::group_by(month=floor_date(date, "month")) %>%
  dplyr::summarize(career=mean(financial_career), restrict=mean(quar_social), health=mean(health_infected), guideline=mean(break_guideline), work=mean(health_work), mental=mean(mental_health), death=mean(death), travel=mean(travelling),future=mean(future)) -> grouped_month_anno

#df.long.month.anno <- gather(grouped_month_anno, varname, value, -month)

ggplot(df.long.month.anno , aes(month)) + 
  geom_line(aes(y = value, colour = varname), size= 1) +
   scale_x_date(date_labels="%b %Y",date_breaks  ="1 month") + 
  # scale_color_brewer(palette="Set1")+ 
  scale_color_manual(values=c("#4DAF4A", "#F786BF", "#FF7F00", "#E41A1C", "#FFD700", "#A65628","#377EB8", "#696969", "#984EA3")) + 
  theme_bw() +
  #theme(text = element_text(size=20)) + theme(legend.position="bottom", legend.box = "horizontal")+
 theme(axis.text.x = element_text(angle = 60, vjust = 0.5), axis.title.x = element_blank())

ggplot(grouped_month_anno, aes(x=month)) +
  
  geom_line(aes(y=career), size=1, color="#4DAF4A") + 
  geom_line(aes(y=restrict), size=1, color="#F781BF") + 
  geom_line(aes(y=health), size=1, color="#FF7F00") + 
  geom_line(aes(y=guideline), size=1, color="#E41A1C") + 
  geom_line(aes(y=work), size=1, color="#FFD700") + 
  geom_line(aes(y=mental), size=1, color="#A65628") + 
  geom_line(aes(y=death), size=1, color="#377EB8") + 
  geom_line(aes(y=travel), size=1, color="#696969") +
  geom_line(aes(y=future), size=1, color="#984EA3") +
  scale_x_date(date_labels="%b %Y",date_breaks  ="1 month") + 
  
  
  scale_y_continuous(
    
    # Features of the first axis
    name = "SOA",
    
    # Add a second axis and specify its features
  
  )+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5), axis.title.x = element_blank())
   


```